---
title: "R Markdown Intro"
author: "Rebecca Cates"
date: "11/4/2019"
output: html_document
---
Include this in R markdown script for it to be applied to all chunks below this chunk


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

some **bold**

*italicized*

CPUE^2^

~~strikethrough~~



# Header 1 

## Header 2

Include a [link](http.nceas.ucsb.edu)

    A full blank space (character turn) between lines is necessary to distinguish between lines in the final knitted document. Adouble space after a line will accomplish the same thing.

* apple

* orange

* pineapple

```{r}

x<-3*4
y<-12

```

# Create an ordered list

Least favorite airports

1. Phoenix  
   * terminal 4   
   * terminal 3   
2. Phoenix  
3. Phoenix  

# Show in-line R code

My results show a value of `r round(y)`

$\sum{x^2}$

# function syntax

result_value<- function_name(argument1 = value, argument2 = value2 ...)
```{r}
weight_kg <- c(55, 25, 12)
mean(weight_kg)
```
```{r}
which(weight_kg <55)
```

# Read data into environment

Use `read.csv` to read in the data

```{r}
bg_chem <- read.csv("BGchem2008data.csv",
                    stringsAsFactors = FALSE)

class(bg_chem)

head(bg_chem)

```

```{r}
mean_depth<-mean(bg_chem$CTD_Depth)

```

```{r}
plot(bg_chem$CTD_Depth, bg_chem$CTD_Temperature)
```

